Tunnels to Towers: Secure Virtual Private Networking for CCN

### 2017-01-31 paper/07-experiment.tex
adding results for up to 300 x 300 consumers/producers. Throughput and packet drop ratio. Figure 6

>>>>

\begin{figure}[!t]
\centering
  \subfigure[Throughtput: Content size 1024B]{\includegraphics[width=1.5in]{images/1024_many_throughput.png}\label{4a}}
  \hfil
  \subfigure[Dropped packets: Content size 1024B]{\includegraphics[width=1.5in]{images/1024_many_dropped.png}\label{4b}}
  \hfil
  \subfigure[Throughtput: Content size 10240B]{\includegraphics[width=1.5in]{images/10240_many_throughput.png}\label{4c}}
  \hfil
  \subfigure[Dropped packets: Content size 10240B]{\includegraphics[width=1.5in]{images/10240_many_dropped.png}\label{4d}}
\caption{Throughput per consumer with massive number of consumers/producers. Each consumer issues 5 interests}\label{exp4}
\end{figure}
